---
title: "Assignment04"
author:
  - "Rui Dong rd1203"
format:
  html:
    embed-resources: true
execute:
  warning: false
  message: false
---

## Introduction

This analysis uses the [Our World in Data-Energy](https://github.com/owid/energy-data) published by University of Oxford. This dataset contains 130 variables across 220 countries from year 1900 to 2025. It covers country-level data on energy use and electricity generation. I look at how energy use relates to income and how much electricity comes from clean and fossil sources respectively, because cleaner electricity is an important part of climate policy.

## Data Preparation

```{r}
library(tidyverse)
library(readr)
owid_energy_data <- read_csv("data/owid-energy-data.csv")
```

```{r}
# Keep only countries (rows without an ISO code are regions like "World" or "Europe")
countries <- owid_energy_data |>
  filter(!is.na(iso_code))

# Five large countries to compare
my_countries <- c("Brazil", "China", "Germany", "India", "United States")
```

## Graph 1: Income and Energy Use

```{r}
countries |>
  filter(year == 2022) |>
  mutate(gdp_per_capita = gdp / population) |>
  ggplot(aes(x = gdp_per_capita, y = energy_per_capita)) +
  geom_point(aes(size = population), alpha = 0.5, color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "orange") +
  scale_x_log10() +
  scale_y_log10() +
  labs(title = "Richer countries use more energy per person",
       subtitle = "GDP per capita and energy use per capita, 2022",
       x = "GDP per capita (international-$, log scale)",
       y = "Energy per capita (Kwh, log scale)",
       size = "Population",
       caption = "Source: Our World in Data Energy Dataset") +
    theme_minimal()
```

#### Each point in this graph is a country, and the size of the point shows its population. Countries with higher GDP per capita use much more energy per person, and most points stay close to the trend line. This means that as poorer countries grow richer, their energy use is likely to rise. 
