---
title: "Assignment04"
author:
  - "Rui Dong rd1203"
format:
  html:
    embed-resources: true
execute:
  warning: false
  message: false
---

## Introduction

This analysis uses the [Our World in Data-Energy](https://github.com/owid/energy-data) published by University of Oxford. This dataset contains 130 variables across 220 countries from year 1900 to 2025. It covers country-level data on energy use and electricity generation. I look at how energy use relates to income and how much electricity comes from clean and fossil sources respectively, because cleaner electricity is an important part of climate policy.

## Data Preparation

```{r}
library(tidyverse)
library(readr)
owid_energy_data <- read_csv("data/owid-energy-data.csv")
```

```{r}
# Keep only countries (rows without an ISO code are regions like "World" or "Europe")
countries <- owid_energy_data |>
  filter(!is.na(iso_code))

# Five large countries to compare
my_countries <- c("Brazil", "China", "Germany", "India", "United States")
```

The `echo: false` option disables the printing of code (only output is displayed).
